---
title: "Workshop Setup Instructions"
author: "Adele B and Paul H"
date: "2022-11-08"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


**IMPORTANT: If you have an M1 Mac - do not follow these instructions, use one of the provided Virtual Machines (VM). Details on how to log on and access the VM will be provided during the workshop.**

## Get the workshop material and data

In RStudio **create a new project**. This ensures all the files for this workshop are placed in their own folder.

Once you've created a new project, run the following R code to download the workshop material and dataset:

```{r eval=FALSE}
## Download files we will be using
options(timeout=3600)
filenames <- c("pbmc3k_tutorial.R", "kang2018.rds")
url <- "https://raw.githubusercontent.com/MonashBioinformaticsPlatform/PBMC-Single-Cell-Workshop-2022/main/vignettes/" 
for(filename in filenames)
    download.file(paste0(url,filename), filename)

## Download and untar the raw data
download.file(
    "http://10x.files.s3-us-west-2.amazonaws.com/samples/cell/pbmc3k/pbmc3k_filtered_gene_bc_matrices.tar.gz",
    "pbmc3k_filtered_gene_bc_matrices.tar.gz")

untar("pbmc3k_filtered_gene_bc_matrices.tar.gz")
```

## Package Installation
 
For this workshop, several packages need to be installed.

BiocManager likes to update installed packages, but we have disabled this in the R code below. If your installation fails, then you might need to turn updates on. Note that if there are a large number of packages that BiocManager wants to update it can take several hours.

These instructions have been tested with R version 4.2.1 and Bioconductor version 3.16.

```{r, eval=FALSE}
## Install required packages for Seurat:
install.packages(c("Seurat", "dplyr", "remotes", "R.utils"))

# 2022-10-30 Harmony failed checks on CRAN. Need to use some old versions for now.
remotes::install_version("RcppArmadillo", version="0.11.2.4.0")
remotes::install_version("harmony", version="0.1", upgrade="never")

## Install required Bioconductor packages
install.packages("BiocManager")
BiocManager::install(c('SingleR', 'celldex',
                       'BiocGenerics', 'DelayedArray', 'DelayedMatrixStats',
                       'limma', 'S4Vectors', 'SingleCellExperiment',
                       'SummarizedExperiment', 'batchelor', 'Matrix.utils'),
                     update=FALSE)

## Install dev versions of some interactive graphics packages
remotes::install_github("plotly/plotly.R")
remotes::install_github("pfh/langevitour")
```

